Working Script

### 2020-09-03 WorkingScript.Rmd
Added a note.
Added some models after talking with Joel.

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = fate))
```

Now, let's run some preliminary analyses:

```{r}
mod1 <- lm(area ~ food + fate, data = data)

@@

>>>>

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = food))
```

Now, let's run some preliminary analyses (this is probably whack because it's bimodal):

```{r}
mod1 <- lm(area ~ food*para*HS + mass.max, data = data)

@@

```{r}
mod2 <- lm(mass.max ~ food*para*HS, data = data)

summary(mod2)
```

```{r}
mod3 <- lm(area ~ mass.max, data = data)

summary(mod3)
```
